Robust Adaptation to Multi-Scale Climate Variability

### 2019-04-10 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
Add line to describe data location.

% Other package calls
\usepackage{
  amssymb, amsmath,   % for math symbols
  apacite,            % AGU style citations apparently
  booktabs,           % for nice tables
  graphicx,           % for figures
  natbib,             % for references
  physics,            % for physics notation
  siunitx,            % for SI notation
  xspace,             % for ie and eg
}

@@

% Some package settings
\sisetup{round-mode=figures,round-precision=3,scientific-notation=false}
\graphicspath{{./figs/}{../fig/}} % folders of figures
\allowdisplaybreaks{} % let the align environment span multiple pages

@@

The authors thank Dr. Alberto Montanari and one anonymous reviewer for insightful comments on this manuscript.
The authors thank Nandini Ramesh of Columbia University for providing the synthetic NINO3 index from a \SI{100000}{year} run of the Cane-Zebiak model as described in \citet{Ramesh:2016hf}.
The authors thank John High of the United States Army Corps of Engineers for providing the naturalized daily streamflows at the Folsom Dam.
JDG thanks the NSF GRFP program (grant DGE 16-44869: ``Understanding \& Predicting Climate Drivers of Extreme, Mid-latitude River Floods'') and SERDP program (grant 2516: ``Climate Informed Estimation of Hydrologic Extremes for Robust Adaptation to Non-Stationary Climate'') for support.

>>>>

% Other package calls
\usepackage{
  amssymb, amsmath,   % for math symbols
  apacite,            % AGU style citations apparently
  booktabs,           % for nice tables
  graphicx,           % for figures
  natbib,             % for references
  physics,            % for physics notation
  siunitx,            % for SI notation
  url,                % show a url
  xspace,             % for ie and eg
}

@@

% Some package settings
\sisetup{round-mode=figures,round-precision=3,scientific-notation=false}
\graphicspath{{./figs/}{../fig/}} % folders of figures

\allowdisplaybreaks{} % let the align environment span multiple pages

@@

The authors thank Dr. Alberto Montanari and one anonymous reviewer for insightful comments on this manuscript.
The authors thank Nandini Ramesh of Columbia University for providing the synthetic NINO3 index from a \SI{100000}{year} run of the Cane-Zebiak model as described in \citet{Ramesh:2016hf}.
The authors thank John High of the United States Army Corps of Engineers for providing the naturalized daily streamflows at the Folsom Dam.
JDG thanks the NSF GRFP program (grant DGE 16-44869: ``Understanding \& Predicting Climate Drivers of Extreme, Mid-latitude River Floods'') and SERDP program (grant 2516: ``Climate Informed Estimation of Hydrologic Extremes for Robust Adaptation to Non-Stationary Climate'') for support.
All codes and data used to generate this paper are available in a live repository at \url{https://github.com/jdossgollin/2018-robust-adaptation-cyclical-risk/} and a permanent archive at \url{https://doi.org/10.5281/zenodo.2634249}.
